Generalized Plackett-Luce Likelihoods

### 2022-09-27 inst/jss_4382.tex
issue #159 issue #160 issue #161

@@

@@

>>>>

\textcolor{blue}{Response: the pattern has been removed as suggested,
  all functions exported are exported explicitly.  However, it is not
  clear who ``the user" is.  Apart from myself, it seems that most
  users of the package are my graduate students who are mostly working
  on applying hyper2 constructions to their own pet datasets; this
  group of users needs to see similar work that they can modify for
  their own projects.  The package was reviewed by Turner in 2020 but
  it is not clear whether she was a user in the sense of the
  comment. In any event, the output of {\tt help(package = "hyper2")}
  is now restricted only to functions that might be of interest to
  users.  }

@@

\textcolor{blue}{Response: spaces added as appropriate}

@@

\textcolor{blue}{Response: done}
